16s lefse

### 2021-03-18 scripts/57_16s_lefse.Rmd
update

```{r}
# sort out the genera counts table and also do filtering (need to have all taxa levels)
meta <- read_csv('../data/amplicon/stool/combined_2_meta.csv')
library(vdbR)
connect_database('~/dbConfig.txt')
get_table_from_database('asv_annotation_blast_ag')
get_table_from_database('asv_counts_ag')
cts <- get_counts_subset(meta$sampleid)

@@

```{r}
pheno <- meta %>% 
  select(cr_d100:crs, )
  gather('pheno', 'value', cr_d100:crs)

@@

all_sub_pheno %>% 
  imap(function(.x, .y){
    select(.data = .x, value) %>% 
      t() %>% 
      write.table(str_glue('../data/shotgun_output/humann3/pull_{.y}.txt'), sep = '\t', quote = F, row.names = T, col.names = F)
  })
```

>>>>

```{r}
library(tidyverse)
```

```{r}
# sort out the genera counts table and also do filtering (need to have all taxa levels)
meta <- read_csv('../data/amplicon/stool/combined_2_meta.csv')
library(vdbR)
connect_database('~/dbConfig.txt')
get_table_from_database('asv_annotation_blast_ag')
cts <- get_counts_subset(meta$sampleid)

@@

```{r}
# the pheno label for the samples
pheno <- meta %>% 
  select(center, cr_d100:crs, icans, sampleid) %>% 
  gather('pheno', 'value', cr_d100:icans)

@@

tpheno <- all_sub_pheno %>% 
  imap(function(.x, .y){
    select(.data = .x, value, center) %>% 
      t() %>% write.table(str_glue('../data/amplicon/lefse/pull_{.y}.txt'), sep = '\t', quote = F, row.names = T, col.names = F)
  })

tcts <- all_sub_pheno %>% 
  map(~ pull(.data = ., sampleid) ) %>% 
  imap(~ cts_genus_fil %>% select(taxa_genus, matches(.x)) %>%  write_tsv(str_glue('../data/amplicon/lefse/{.y}_tcts.tsv'))) 
```

cat pull_toxicity.txt toxicity_tcts.tsv > pull_toxicity_tcts.tsv
cat pull_cr_d100.txt cr_d100_tcts.tsv > pull_cr_d100_tcts.tsv 
cat pull_crs.txt crs_tcts.tsv > pull_crs_tcts.tsv
cat pull_icans.txt icans_tcts.tsv > pull_icans_tcts.tsv

```{r}
fns <- list.files('../data/amplicon/lefse/', pattern = 'pull.*_tcts.tsv$')

cmds <- tibble(
  fns = fns
) %>% 
  mutate(format_cmd = str_glue('format_input.py {fns}  {fns}.in -c 1 -s 2  -u 3  ')) %>% 
  mutate(run_cmd = str_glue('run_lefse.py {fns}.in  {fns}.res')) %>% 
  mutate(plot_cmd = str_glue('plot_res.py {fns}.res {fns}.png  --feature_font_size 4 --width 10 --dpi 300 --title {fns}')) %>% 
  mutate(clado_cmd = str_glue('plot_cladogram.py {fns}.res {fns}_clado.pdf  --label_font_size 4 --dpi 300 --format pdf --title {fns}')) %>% 
  select(-fns) %>% 
  gather() %>% 
  select(value) %>% 
  write_csv('../data/amplicon/lefse/lefse_run_cmd_taxa.sh', col_names = F)

# No differentially abundant features found in the 4
# also this is the case when using center as subclass 
```
